Distinguish Real and Fake UHD Images with Relative Discrete Cosine Transform (RDCT)

### 2019-12-22 3-UHD/report/paper.tex
some intro

\section{Introduction}
\IEEEPARstart{T}{his}

@@

\subsection{A Naive Thought: Enumerative Search}
\cref{sec:enumerative}
We first try to tackle the problem with a very naive approach.
If we know all possible ways to generate false UHD images, assuming the number of them is limited, we can actually enumerate through all of them to determine which algorithm is applied in any given false UHD image.

>>>>

\section{Introduction}
\IEEEPARstart{U}tral-High Definition images refer to images with extremely high definitions.
A common UHD is 4K resolution, which includes many definitions, one of which is 3840*2160 and is the images under the consideration of this project.

@@

\subsection{A Naive Thought: Enumerative Search}
\label{sec:enumerative}
We first try to tackle the problem with a very naive approach.
If we know all possible ways to generate false UHD images, assuming the number of them is limited, we can actually enumerate through all of them to determine which algorithm is applied in any given false UHD image.
